MCC Models

### 2019-04-03 papers/full_paper/SI_appendix.Rmd
first draft full paper

ggplot(data = child_cor_plot,aes(x = model_mode, y = data_mode, col = age)) +
  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
  geom_point(size = 3)+
  geom_errorbar(aes(ymin = data_ci_lower, ymax = data_ci_upper),width = 0,size = .7)+
  geom_errorbarh(aes(xmin = model_ci_lower, xmax = model_ci_upper), height = 0,size = .7)+
  coord_fixed()+
  facet_grid(~model)+
  stat_cor(method = "pearson", label.x = 0.01, label.y = 0.99, aes(x = model_mode, y = data_mode), inherit.aes = F)+
  xlim(0,1)+ylim(0,1)+
  xlab("Model")+
  theme_few() + 
  scale_colour_ptol()
```

>>>>

ggplot(data = child_cor_plot,aes(x = model_mode, y = data_mode, col = age)) +
  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
  geom_point(size = 3)+
  geom_errorbar(aes(ymin = data_ci_lower, ymax = data_ci_upper),width = 0,size = .7)+
  geom_errorbarh(aes(xmin = model_ci_lower, xmax = model_ci_upper), height = 0,size = .7)+
  coord_fixed()+
  facet_grid(~model)+
  stat_cor(method = "pearson", label.x = 0.01, label.y = 0.99, aes(x = model_mode, y = data_mode), inherit.aes = F)+
  xlim(0,1)+ylim(0,1)+
  xlab("Model")+
  ylab("Data")+
  theme_few() + 
  scale_colour_ptol()
```

### 2019-04-03 papers/full_paper/manuscript.Rmd
first draft full paper

---
title             : "Predicting the integration of social information in pragmatic word learning across development"

@@

author_note: |
  MB received funding from the European Union’s Horizon 2020 research and innovation programme under the Marie Sklodowska-Curie grant agreement no. 749229.

abstract: |
  Enter abstract here. Each new line herein must be indented, like this line.

@@

Language use as and learning  integration of different sources of information. Next to conventional syntax and semantics, expectations about communicative interactions play a decisive role. These expectations can be considered on two levels. on the one hand, general expectations that apply to any interlocutor. On top of this there is information that is particular to a specific speaker which is included in the common ground between interlocutors. This generates specific expectations .

Knowledge of communicative conventions such as words in a language could also be considered as (cultural) common ground information, generating certain expectations about communicative behavior

In practice, communication requires balancing and integrating these different sources of information. RSA bla bla

From a developmental perspective

took a truyl developmental perspective in a

@@

In the novelty manipulation (Fig 1B - right), the speaker encountered one object on one of the tables. Later, a second object appeared. The second object was therefore new to the speaker. When the same speaker later used a novel word to requested an object (in a slightly excited way), participants could infer that it was the new object they are referring to. In contrast, when a different speaker, tho whom both objects were equally new, made a request, no inference could be made based on the speaker's state of knowledge. In line with this reasoning, participants selected the new object above chance with the same speaker (t(`r ex2tnov%>%filter(condition == "same_speaker")%>%pull(df)`) = `r ex2tnov%>%filter(condition == "same_speaker")%>%pull(t_value)`, *p* `r ex2tnov%>%filter(condition == "same_speaker")%>%pull(p_value)`, see Fig. 2), and more often compared to the different speaker ($\beta$ = `r ex2nov_r%>%filter(term == "conditionsame_speaker")%>%pull(estimate)`, se = `r ex2nov_r%>%filter(term == "conditionsame_speaker")%>%pull(std.error)`, *p* `r ex2nov_r%>%filter(term == "conditionsame_speaker")%>%pull(p.value)`). Taken together, experiment 1 and 2 showed that adults use general and speaker specific expectations to identify the referent of a novel word. In the following, we studied how these expectations are integrated when combined experimentally.

@@

prior as change in salience

Development is reflected as change in each expectation, the process of integration is assumed to be the same. this could be changed in the future

bring down noise level for 3yo when testing between subjects?

>>>>

---
title             : "Predicting information integration in pragmatic word learning across development"

@@

author_note: |
  MB received funding from the European Union’s Horizon 2020 research and innovation programme under the Marie Sklodowska-Curie grant agreement no. 749229. We thank Jacqueline Quirke, Sabina Zacco and especially Megan Merrick for help with the data collection.

abstract: |
  Language is used and learned in complex social settings. To infer what a speaker means, listeners have to go beyond the literal meaning of words and rely on pragmatic inferences. During language acquisition, the same processes can help children to learn the meaning of novel words. Yet, pragmatic inferences require balancing multiple sources of social information. Here we study this integration process. We isolate two types of pragmatic inference and formalize how they should be integrated in a Bayesian pragmatics model. We present a series of experiments with preschool children and adults that suggest that information integration is best described as a form of probabilistic inference.

@@

Language use and language learning require integrating and balancing different sources of information. And even though linguistic cues, such as conventional syntax and semantics, may provide strong evidence about the intended meaning of an utterance, additional pragmatic inferences are necessary arrive at a precise interpretation [@levinson2000presumptive; @sperber2001relevance]. A second route to meaning is even more important in the process of language learning. In this case, inferences based on the social embedding of the utterance are key to understanding its meaning and learning the words contained therein [@clark2009first; @tomasello2009constructing]. In this paper, we explore how different forms of social information are integrated during word learning across development. More specifically, we look at information integration as a form of probabilistic inference.

Pragmatic inferences rest on assumptions about how communication *should* proceed. Interlocutors mutually expect each other to communicate in a cooperative way and this mutual expectation serves as the basis for inferences that go beyond the literal meaning of an utterance [@grice1991studies; @sperber2001relevance; @tomasello2008origins]. Paul Grice [-@grice1991studies] famously summarized this notion in his *Cooperative Principle*, which reads: “Make your contribution such as is required, at the stage at which it occurs, by the accepted purpose or direction of the talk exchange in which you are engaged.” Two sets of expectations follow from this principle. On the one hand, there is the general expectation that one follows the principle and communicates in a relevant and informative way. On the other hand, there is the expectation that communication is further specific to the communicative partner, that is, that it is adjusted to the the common ground shared between speaker and listener [@bohn2018common; @clark1996using].

Importantly, these expectations can also support language development [@clark2009first; @tomasello2009constructing]. Starting in infancy, children generally expect adults' communicative acts to provide them with relevant information [e.g @behne2005one]. And preschool children learn novel words by assuming that speakers are informative [@frank2014inferring]. In the absence of any additional information about the potential referent objects or the speaker, children expected a novel word to be intended to refer to an object it describes in a unique way [see also @stiller2015ad]. Person specific common ground information supports communication in infancy [e.g. @bohn2018social; @saylor2011s] and facilitates word learning in slightly older children. For example, two-year-olds keep track of which object is new to a speaker to decide which object the speaker is referring to when they use a novel word [@akhtar1996role; @diesendruck2004two]. Furthermore, when three to five year old children learn about a speaker's preference, they later use this information to identify the meaning of an unknown word coming from the same speaker [@saylor2009preschoolers]. These studies suggest early emerging pragmatic competences. Yet, communicative interactions in naturalistic contexts have multiple layers and require balancing expectations [@clark1996using]. So how are different expectations integrated?

The Rational Speech Act (RSA) framework [@frank2012predicting; @goodman2016pragmatic] offers a formal framework for addressing this integration problem. RSA models are characterized by their recursive structure. Each agent in the recursion is modeled as a Bayesian reasoner; thus, information integration is treated as a process of probabilistic inference. The expectation that speakers communicate informatively is already encoded in the structure of the model: Speakers choose utterances that help listeners in disambiguating referents. Common ground information can be integrated in the model as a shared prior probability of referents in the context of the utterance. Thus, a natural locus for information integration within RSA models is the trade off between the prior probability of a referent and the likelihood of that referent given the current utterance.

Here we apply this rational, pragmatic account of communication to the study of information integration during word learning. We do so from a developmental perspective and include children, continuously sampled between three and five years of age, as well as adults. For both groups, we first test speaker-specific and common ground expectations independently. Based on this data, we generate model predictions about how expectations should be integrated. Finally, we compare these predictions to newly collected data and use model comparisons to test different hypothesis about how expectations are integrated.

@@

In the novelty manipulation (Fig 1B - right), the speaker encountered one object on one of the tables. Later, a second object appeared. The second object was therefore new to the speaker. When the same speaker later used a novel word to requested an object (in a slightly excited way), participants could infer that it was the new object they are referring to. In contrast, when a different speaker, to whom both objects were equally new, made a request, no inference could be made based on the speaker's state of knowledge. In line with this reasoning, participants selected the new object above chance with the same speaker (t(`r ex2tnov%>%filter(condition == "same_speaker")%>%pull(df)`) = `r ex2tnov%>%filter(condition == "same_speaker")%>%pull(t_value)`, *p* `r ex2tnov%>%filter(condition == "same_speaker")%>%pull(p_value)`, see Fig. 2), and more often compared to the different speaker ($\beta$ = `r ex2nov_r%>%filter(term == "conditionsame_speaker")%>%pull(estimate)`, se = `r ex2nov_r%>%filter(term == "conditionsame_speaker")%>%pull(std.error)`, *p* `r ex2nov_r%>%filter(term == "conditionsame_speaker")%>%pull(p.value)`). Taken together, experiment 1 and 2 showed that adults use general and speaker specific expectations to identify the referent of a novel word. In the following, we studied how these expectations are integrated when combined experimentally.

@@

Integrating different sources of information is an integral part of human communication. To infer the intended meaning of an utterance, listeners combine their knowledge of communicative conventions (semantics and syntax) with social expectations about their interlocutor. When learning new words, social information is especially vital. But how are different social expectations integrated during word learning? Here we explored the hypothesis that information integration is a process of probabilistic inference. We studied how expectations that speakers communicate in an informative way are contextualized by expectations that follow from prior interactions with the speaker. Across development, participants' learning was best predicted by a Bayesian pragmatics model in which expectations were flexibly traded-off between one another in a probabilistic way. Alternative models, which considered only one type of expectation, made worse predictions.

The pragmatics model goes beyond simply weighing expectations by some ratio. It offers an explicit account about how integration may proceed: Because all objects are new and their labels unknown, the initial probability of each object depends entirely on common ground information. Now, the listener assumes the speaker to produce their utterance based on the expected effect that their utterance will have *in light of* this shared common ground. Thus, inferences are not computed separately but the result of an integrated process.

In the current model, common ground information was treated in the same way as contextual salience [see e.g. @frank2012predicting]. Interacting around an object changed the probability that this object will be communicated about. In theory, similar changes could be brought about by increasing the object's perceptual salience. Future work could try to explicitly model the social-cognitive processes that gave rise to common ground expectations and contrast social and perceptual salience.

We conceptualized developmental change as age related changes in the propensity to make the individual inferences. That is, while the degree to which listeners expect speakers to be informative or follow common ground changes with age, the process by which expectations are integrated remains the same. This is a very parsimonious conception of developmental change and others, in which the integration process itself changes with age, are also plausible and worth exploring.

Studying how multiple types of social information are balanced contributes to a comprehensive and ecologically valid model of word learning. In the current study, participants inferred the referent by integrating non-linguistic cues (speakers turning and looking to one table) with assumptions about speaker informativeness and common ground information. However, in addition to social information, children can use semantic and syntactic features of the utterances as cues to the meaning of the words embedded therein [e.g. @clark1973s; @abend2017bootstrapping; @gleitman1990structural]. The everyday learning environment is complex and combines non-linguistic, linguistic as well as pragmatic cues. Across development, children learn to recruit these different sources of information and integrate them. Our studies show how computational models of language use and comprehension can be used as powerful tools to explicate and test hypothesis about how integration proceeds.
